\section{Problem Sets}
\begin{itemize}
    \item Problem set due dates will be posted with each assignment.  
    \item Late problem sets will not be accepted unless (1) Short Term Illness
        prevents completion, or (2) arrangements are made \emph{in advance}
        with Dr. Palmeri.
    \item Unless otherwise stated, all assignments are due in the \verb+BME354L (Nightingale)+ 
        grader box on the second floor of the Hudson Hall Annex at the
        specified time.  
    \item Please make sure that your submitted problem sets are clearly labeled
        with your name, problems are clearly numbered, and the pages are
        secured with a staple or paper/binder clip.  You can't receive credit
        for missing pages!
    \item When solving circuit analysis problems in the assignments:
        \begin{itemize}
            \item Always draw the circuit/diagram for each problem involving a
                circuit/diagram.
            \item Label all circuit elements with symbols.  Solve problems
                symbolically before substituting in numerical values.
            \item Please write legibly and include all relevant steps in
                arriving at your solution.
            \item Please place a box around all final solutions.
            \item Attach any computer code (e.g., Matlab code) used to solve
                problems.  Place comments in the code where appropriate to
                indicate your thought process.
            \item \textbf{All answers must have units.}  No units = No credit!
            \item All graphs must have appropriately labeled axes/legends with
                units.
        \end{itemize}
\end{itemize}
