\section{Words of Wisdom}
\begin{itemize}
    \item Check Sakai often for assignments, lab-related documents, and other
    important class information.
    \item Make the most out of attending lecture... briefly review notes from
    the previous lecture before class and make sure that you're understanding
    the ``why'', not just the ``what''. For example, instead of just memorizing
    that current and voltage lead/lag one another in capacitive/inductive
    devices, make sure that you understand the physics behind those behaviors.
    Remembering the lead/lag relations becomes a lot easier when you know why
    they exist.
    \item Don't wait until the last minute to do the problem sets!! They're
    designed to provide you with opportunities to figure out what you do and
    don't know; leaving them until the last minute compromises that objective.
    Working on problem sets in advance will also provide a catalyst to...
    \item Ask questions and attend office hours. BME354L is your opportunity to
    learn about medical device electronics. Take advantage of your instructors
    and TAs to help your learn this material--we're here for you!
    \item Feedback is a two-way street. I'll let you know how you are doing
    throughout the semester, and in return, you should feel free to let me know
    what you are or are not understanding. I'd rather cover less material that
    you understand well than covering lots of material that you'll forget
    sooner rather than later.
\end{itemize}
